Depletion capabilities in the OpenMC Monte Carlo particle transport code

### 2020-06-24 manuscript.tex
Mention why FPs were chosen

\Cref{fig:pwr-actinides-full} shows the relative difference in predicted
actinide concentrations between OpenMC and Serpent at four different burnup
values. We see that most of the differences are less than 0.1\%, and all are
within 0.15\%. The differences in $^{235}$U and $^{239}$Pu concentrations
increase slightly with increasing burnup, which most likely accounts for the 20
pcm difference observed for the full chain in \cref{fig:pwr-keff}. While not
shown, the predicted actinide concentrations for the reduced chain are nearly
identical to those observed for the full chain in \cref{fig:pwr-actinides-full}.
\Cref{fig:pwr-actinides-casl} shows the differences in actinide concentrations
using the CASL depletion chain. Because the CASL depletion chain differs from
the full depletion chain primarily with respect to how fission products are
treated, the differences reported in \cref{fig:pwr-actinides-casl} closely
mirror those in \cref{fig:pwr-actinides-full}.
\begin{figure}[H]
  \centering
  \includegraphics[width=4in]{figures/pwr/pwr_actinides_full.pdf}
  \caption{Relative difference in actinide concentrations between OpenMC and
  Serpent for the PWR pincell model at 5, 12.5, 30, and 50 MWd/kg using the full
  depletion chain.}
  \label{fig:pwr-actinides-full}
\end{figure}
\begin{figure}[H]
  \centering
  \includegraphics[width=4in]{figures/pwr/pwr_actinides_casl.pdf}
  \caption{Relative difference in actinide concentrations between OpenMC and
  Serpent for the PWR pincell model at 5, 12.5, 30, and 50 MWd/kg using the CASL
  depletion chain.}
  \label{fig:pwr-actinides-casl}
\end{figure}

>>>>

\Cref{fig:pwr-actinides-full} shows the relative difference in predicted
actinide concentrations between OpenMC and Serpent at four different burnup
values. The fission products that are shown in \cref{fig:pwr-actinides-full}
have been chosen because they are either strong neutron absorbers or significant
contributors to decay heat and/or radiotoxicity. We see that most of the
differences are less than 0.1\%, and all are within 0.15\%. The differences in
$^{235}$U and $^{239}$Pu concentrations increase slightly with increasing
burnup, which most likely accounts for the 20 pcm difference observed for the
full chain in \cref{fig:pwr-keff}. While not shown, the predicted actinide
concentrations for the reduced chain are nearly identical to those observed for
the full chain in \cref{fig:pwr-actinides-full}. \Cref{fig:pwr-actinides-casl}
shows the differences in actinide concentrations using the CASL depletion chain.
Because the CASL depletion chain differs from the full depletion chain primarily
with respect to how fission products are treated, the differences reported in
\cref{fig:pwr-actinides-casl} closely mirror those in
\cref{fig:pwr-actinides-full}.
\begin{figure}[H]
  \centering
  \includegraphics[width=4in]{figures/pwr/pwr_actinides_full.pdf}
  \caption{Relative difference in actinide concentrations between OpenMC and
  Serpent for the PWR pincell model at 5, 12.5, 30, and 50 MWd/kg using the full
  depletion chain.}
  \label{fig:pwr-actinides-full}
\end{figure}
\begin{figure}[H]
  \centering
  \includegraphics[width=4in]{figures/pwr/pwr_actinides_casl.pdf}
  \caption{Relative difference in actinide concentrations between OpenMC and
  Serpent for the PWR pincell model at 5, 12.5, 30, and 50 MWd/kg using the CASL
  depletion chain.}
  \label{fig:pwr-actinides-casl}
\end{figure}
